Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2020-08-20 mice_synthesizing/Mice_Synthesizing.Rmd

```{r, echo = T}
broom::tidy(truemodel, conf.int=TRUE) %>%
  mutate(CIW = conf.high - conf.low) %>% 
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

```{r, message = F}
bind_rows("Mice default" = results_def,
          "Mice with cart" = results_cart, .id = "Imputation method") %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

```{r, message = F}
ci_cov(pooled, truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

```{r, message = F}
true_results <- bootstrap_boys %>%
  map(~ lm(wgt ~ age + hgt, .x)) %>%
  map_dfr(~ broom::tidy(.x, conf.int = TRUE)) %>%
  mutate(true_coef = rep(coef(truemodel), nsim),
         true_se   = rep(sqrt(diag(vcov(truemodel))), nsim),
         cover     = conf.low < true_coef & true_coef < conf.high) %T>% 
  assign("boot_true", ., envir = globalenv()) %>%
  group_by(term) %>%
  summarise("True Est" = unique(true_coef),
            "Boot Est"  = mean(estimate),
            "Bias"     = mean(estimate - true_coef),
            "True SE"  = unique(true_se),
            "Boot SE"   = mean(std.error),
            "DF"       = 745,
            "Lower"    = mean(conf.low),
            "Upper"    = mean(conf.high),
            "CIW"      = mean(conf.high - conf.low),
            "Coverage" = mean(cover)) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

synthetic_results <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %T>% 
  assign("boot_syn", ., envir = globalenv()) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

ggplot(plot_dat, aes(x = est, color = Method, fill = Method)) +
  geom_density(alpha = .7) +
  facet_wrap(~ term, nrow = 1, scales = "free") +
  scale_color_viridis_d(begin = .30, end = .65) +
  scale_fill_viridis_d(begin = .30, end = .65) +
  theme_classic()
```

@@

```{r, message = F}
boot_se <- boot_true %>% group_by(term) %>% summarise("Bootstrapped SE" = sd(estimate))
boot_syn_se <- boot_syn %>% group_by(term) %>% summarise("Synthetic bootstrapped SE" = sd(est))

@@

```{r, fig.fullwidth = TRUE, dpi = 1000}
ggplot(plot_dat, aes(x = ciw, color = Method, fill = Method)) +
  geom_density(alpha = .7) +
  facet_wrap(~ term, nrow = 1, scales = "free") +
  scale_color_viridis_d(begin = .30, end = .65) +
  scale_fill_viridis_d(begin = .30, end = .65) +
  theme_classic()
```

@@

```{r}
syns_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

```{r}
boot_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

```{r}
boot_cart_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

bind_rows("Cart default" = cart_default,
          "Cart with adjusted settings and maxit = 1" = cart_adj_maxit,
          "Cart adjusted settings" = cart_adj, .id = "Method") %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

>>>>

```{r, echo = T}
broom::tidy(truemodel, conf.int=TRUE) %>%
  mutate(CIW = conf.high - conf.low) %>% 
  kable(digits = 3,
        caption = "Results of a single linear regression model on the completed dataset.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

```{r, message = F}
bind_rows("Mice default" = results_def,
          "Mice with cart" = results_cart, .id = "Imputation method") %>%
  kable(digits = 3,
        caption = "Results of with mice default settings, and with CART settings, for the imputation of synthetic data, with the in-build mice pooling function.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

```{r, message = F}
ci_cov(pooled, truemodel) %>%
  kable(digits = 3,
        caption = "Imputation results of synthesizing by means of CART, with the pooling rules by Drechsler.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

```{r, message = F}
true_results <- bootstrap_boys %>%
  map(~ lm(wgt ~ age + hgt, .x)) %>%
  map_dfr(~ broom::tidy(.x, conf.int = TRUE)) %>%
  mutate(true_coef = rep(coef(truemodel), nsim),
         true_se   = rep(sqrt(diag(vcov(truemodel))), nsim),
         cover     = conf.low < true_coef & true_coef < conf.high) %T>% 
  assign("boot_true", ., envir = globalenv()) %>%
  group_by(term) %>%
  summarise("True Est" = unique(true_coef),
            "Boot Est"  = mean(estimate),
            "Bias"     = mean(estimate - true_coef),
            "True SE"  = unique(true_se),
            "Boot SE"   = mean(std.error),
            "DF"       = 745,
            "Lower"    = mean(conf.low),
            "Upper"    = mean(conf.high),
            "CIW"      = mean(conf.high - conf.low),
            "Coverage" = mean(cover)) %>%
  kable(digits = 3,
        caption = "Bootstrapped estimates of regression coefficients, with mean standard error and coverage based on the individual estimates of the standard error.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

synthetic_results <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %T>% 
  assign("boot_syn", ., envir = globalenv()) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3,
        caption = "Synthetic (CART) results with pooling rules by Drechsler.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

ggplot(plot_dat, aes(x = est, color = Method, fill = Method)) +
  geom_density(alpha = .7) +
  facet_wrap(~ term, nrow = 1, scales = "free") +
  scale_color_viridis_d(begin = .30, end = .65) +
  scale_fill_viridis_d(begin = .30, end = .65) +
  theme_classic() +
  ggtitle("Distribution of the bootstrapped and synthetic regression coefficients.")
```

@@

```{r, message = F}
boot_se <- boot_true %>% group_by(term) %>% summarise("Mean bootstrapped SEs" = sd(estimate))
boot_syn_se <- boot_syn %>% group_by(term) %>% summarise("Mean synthetic SEs" = sd(est))

@@

```{r, fig.fullwidth = TRUE, dpi = 1000}
ggplot(plot_dat, aes(x = ciw, color = Method, fill = Method)) +
  geom_density(alpha = .7) +
  facet_wrap(~ term, nrow = 1, scales = "free") +
  scale_color_viridis_d(begin = .30, end = .65) +
  scale_fill_viridis_d(begin = .30, end = .65) +
  theme_classic() +
  ggtitle("Distribution of the confidence interval width (CIW) of the bootstrapped and the synthetic datasets.")
```

@@

```{r}
syns_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3,
        caption = "Synthesizing the same data.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

```{r}
boot_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3,
        caption = "Synthesizing bootstrap samples with adjusted imputation settings.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

```{r}
boot_cart_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3,
        caption = "Synthesizing bootstrap samples with adjusted imputation settings but with maxit = 5.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

bind_rows("Cart default" = cart_default,
          "Cart with adjusted settings and maxit = 1" = cart_adj_maxit,
          "Cart adjusted settings" = cart_adj, .id = "Method") %>%
  kable(digits = 3,
        caption = "Within, between and total imputation variance for default CART, and adjusted CART.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### 2020-08-20 mice_synthesizing/paper.Rmd
Added points to discuss.

@@

The R-package `mice` [@mice] implements the fully conditional specification approach for missing data. Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper. In the next section, the pooling rules that are required to obtain inferences from the synthetic datasets are discussed. Thereafter, it will be shown that creating confidence valid [TO DO: FULLY/PARTIALLY] synthetic data can be generated by means of `mice`. Also, it is shown that iterating over the conditional distributions in order to establish convergence is not required, due to the fact that new values are drawn directly from posterior distribution given the observed data.

@@

@@

@@

Discuss mice, predominantly the imputation algorithm in greater depth

>>>>

# OUTLINE

**Intro**

- Motivation/relevance
- Synthetic data (fully/partially shortly explained)
- How can this data be generated in practice (FCS - multivariate synthetic values)
- Mice adopts FCS for missing data
- It will be shown that mice is also capable of generating multivariate synthetic data
- However, multiple rules for correct variance estimates have been proposed, but the choice of one optimal variance estimate is not straightforward. Therefore, the performance of the currently available variance estimators (as outlined below) will be contrasted
- Goal: explain and show how `mice` can be used to create synthetic versions of the data at hand, and which variance estimator yields the best results.

**Synthetic data explained**

*Fully synthetic data*

- Explain the idea in more depth than in the intro
- Explain pooling rules by Raghunathan, Reiter & Rubin
- Adjusted variance estimate by Reiter (restricted positive)
- Simple variance estimator by `synthpop` authors.

*Partially synthetic data*
- Explain the idea in more depth than in the intro
- Explain pooling rules by Reiter.
- Adjusted estimate by `synthpop` authors.

**Mice**

- Explain algorithm (FCS) in more depth
- Observed values can be regarded as starting values for the imputation model. Since the observed data is used for creating the imputation models, no iterations are required. That is, the model is fixed, and not dependent on the imputed values.

**Methods**

- Boys dataset, considering using another dataset (two datasets with same results would prove the point even more).
- Explain synthesizing procedure (by means of cart, using fcs as implemented in mice).
- Imputation settings (CART, as proposed by Reiter).
- What will be looked at: simple means / variances of variables (univariate relationships) and estimates of regression coefficients (of multiple models (at least 2 different models)).
- Eventually: distinction between fully (everything replaced) and partially (only subset of variables replaced) synthetic data. 
- Eventually: distinction between number of imputations (however, $m = 5$ proved to yield sufficient results already in the simulations run thus far).

**Results**

- Discuss results.

**Discussion**

Pros and cons of different methods, theoretically and practically.

@@

The R-package `mice` [@mice] implements the fully conditional specification approach for missing data. Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper. In the next section, the pooling rules that are required to obtain inferences from the synthetic datasets are discussed. Thereafter, it will be investigated which variance estimator yields the best, that is, confidence valid, results in combination with the `mice` synthesizing approach. Also, it is shown that iterating over the conditional distributions in order to establish convergence is not required, due to the fact that new values are drawn directly from posterior distribution given the observed data.

@@

## Fully synthetic data

@@

Explain pooling rules (variance estimates + adjusted variance estimates + simple estimator proposed by synthpop authors)

## Partially synthetic data

Explain pooling rules (variance estimates)

@@

- Discuss mice, predominantly the imputation algorithm in greater depth
- Procedure: observed values can be regarded as starting values, so that all variables can be used for the synthesis of all other variables.
